Wealth dynamics in the presence of network structure and primitive cooperation

### 2019-10-22 manuscript/specnet_cssa19.tex
very minor edits

\begin{itemize}
\item $v$ is the wealth growth rate (the difference of the income and metabolic rate of the agent) and $D$ is the intensity of the Brownian process (white noise process) $w$. 
\item $x(t)$ is the state of the particle (wealth) at time $t$. 
\item The dynamics can be started at any initial point $x_0 > 0$. 
\end{itemize}
Structure
\begin{itemize}
\item Erd\H{o}s-R\'{e}nyi network (ER) models
\end{itemize}
\end{frame}

\begin{frame}[t]
\frametitle{Vocabulary}
\begin{itemize}
\item proto
\end{itemize}
\end{frame}

@@

\begin{frame}[t]
\frametitle{Results}
%% need to link the figures here 
\begin{itemize}
\item Larger environmental noise produces large inequality measures (Figure 1)
\item Larger the noise, larger the separation between the mean lifetimes of the two populations (Figures 2 and 3) 
\item Larger connectivity leads to a more egalitarian population
\item Larger connectivity leads to larger separation between the mean lifetimes of the two populations
\end{itemize}

@@

\begin{frame}[t]
\frametitle{Conclusion}
\begin{itemize}
\item These are very preliminary results 
\item Repeating these simulations on other baseline network models might provide more clarity
\item These models might be amenable to mean field analysis 
\end{itemize}
More generally
\begin{itemize}
\item Our models are an useful addition to the variety of dynamical system models on networks 
\item Despite their simplicity, the exhibit interesting dynamics and are useful to study the two-way interaction between structure and dynamics.  
\end{itemize}
\end{frame}

>>>>

\begin{itemize}
\item $v$ is the wealth growth rate (the difference of the income and metabolic rate of the agent) and $D$ is the intensity of the Brownian process (white noise process) $w$. 
\item $x(t)$ is the state of the particle (wealth) at time $t$. 
\item The dynamics can be started at any initial point $x_0 > 0$ (diffusion on a \textit{semi-infinite interval}. 
\end{itemize}
Structure
\begin{itemize}
\item Erd\H{o}s-R\'{e}nyi network (ER) models
\end{itemize}
\end{frame}

\begin{frame}[t]
\frametitle{Vocabulary}
\begin{itemize}
\item isolates
\item proto a.k.a proto-institutions
\item starvation shock 
\item lifetime 
\item $\lambda$ parameter 
\item \texttt{julia}
\end{itemize}
\end{frame}

@@

\begin{frame}[t]
\frametitle{Results}
%% need to link the figures here 
\begin{itemize}
\item Larger environmental noise produces larger inequality measures (Figure 1)
\item Larger the noise, larger the separation between the mean lifetimes of the two populations (Figures 2 and 3) 
\item Larger connectivity leads to a more egalitarian population
\item Larger connectivity leads to larger separation between the mean lifetimes of the two populations
\end{itemize}

@@

\begin{frame}[t]
\frametitle{Conclusion}
\begin{itemize}
\item These are very preliminary results 
\item Repeating these simulations on other baseline network models might provide more clarity
\item Simulations with SDS models used in macroeconomics will help empirically ground the models  
\item These models might be amenable to mean field analysis 
\end{itemize}
More generally
\begin{itemize}
\item Our models are an useful addition to the variety of dynamical system models on networks 
\item Despite their simplicity, the exhibit interesting dynamics and are useful to study the two-way interaction between structure and dynamics.  
\end{itemize}
\end{frame}
